Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-06-01 manuscript/manuscript.Rmd
rendered with output table

################################################################################
# Condtional Probability
################################################################################
mc_guides <- c(0.3, 1, 1.6, 2, 4, 10, 20)
mc_names <- c("EPA_Child","WHO","EPA_Adult","WHO","WHO","WHO","WHO")

epa_child_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[1]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)
who_drink_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[2]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)
epa_adult_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[3]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)
who_rec_low1_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[4]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)
who_rec_low2_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[5]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)
who_rec_med1_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[6]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)
who_rec_med2_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[7]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

```

@@

>>>>

################################################################################
# Condtional Probability
################################################################################
mc_guides <- c(0.3, 1, 1.6, 2, 4, 10, 20)
mc_names <- c("EPA_Child","WHO","EPA_Adult","WHO","WHO","WHO","WHO")
mc_chla <- vector("numeric",length(mc_guides))

epa_child_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[1]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

mc_chla[1] <- get_chla(epa_child_cp,0.5)

who_drink_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[2]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

mc_chla[2] <- get_chla(who_drink_cp,0.5)

epa_adult_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[3]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

mc_chla[3] <- get_chla(epa_adult_cp,0.5)

who_rec_low1_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[4]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

mc_chla[4] <- get_chla(who_rec_low1_cp,0.5)

who_rec_low2_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[5]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

mc_chla[5] <- get_chla(who_rec_low2_cp,0.5)

who_rec_med1_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[6]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

mc_chla[6] <- get_chla(who_rec_med1_cp,0.5)

who_rec_med2_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log(mc_guides[7]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

mc_chla[7] <- get_chla(who_rec_med2_cp,0.5)
```

@@

```{r mc_chla_table, echo=FALSE}
mc_chla_tbl <- data.frame(Source=mc_names,Microcystin=mc_guides,Chlorophyll=mc_chla)
pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```

### 2015-06-01 manuscript/manuscript.tex
rendered with output table

>>>>

\begin{verbatim}
## 
## -------------------------------------
## Source    Microcystin   Chlorophyll  
## --------- ------------- -------------
## EPA_Child 0.3           23.68        
## 
## WHO       1             65.2         
## 
## EPA_Adult 1.6           79.8         
## 
## WHO       2             113.1        
## 
## WHO       4             273.6        
## 
## WHO       10            338.4        
## 
## WHO       20            338.4        
## -------------------------------------
\end{verbatim}
